---
title: "p8105 HW5 - Sara Kramer (sk4970)"
output: github_document
---

```{r, include = FALSE,message=FALSE,warning=FALSE}
library(tidyverse)
library(readr)
library(lubridate)
library(ggplot2)
library(ggridges)
library(patchwork)
library(rvest)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1
The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 
 

# Problem 2
```{r}
# importing data
homicide = read.csv("./data/problem_2/homicide-data.csv") %>%
  janitor::clean_names() 

# There are 12 variables and 52,179 observations. Variables include report date, victim name (first, last), victim age, victim race, victim sex, multiple variables on location including latitude/longitude, and notes. I noticed a possible error in an observation with one city/state. It was Tulsa, AL. I changed the AL state to OK as I assume that's what it was meant to be. See below. 

# fixing error in a city/state match up
homicide %>%
  mutate(state = if_else(city == "Tulsa" & state == "AL", "OK", state))

# making city_state variable
homicide$city_state <- paste(homicide$city, homicide$state, sep = ", ") 

# creating homi_unsol disp=closed w/o arrest or open/no arrest and homi_total
homicide %>%
  homi_unsolved = case_when(disposition == "Closed without arrest" ~ "unsolved", disposition == "Open/No arrest" ~ "unsolved", TRUE ~ NULL) %>%
  homi_total = 52179

# prop test for Baltimore, MD
balt_prop = 
  filter(city_state = "Baltimore, MD") %>%
  prop.test(
    x = homicide %>% pull(homi_unsolved),
    n = homicide %>% pull(homi_total),
    alternative = c("two.sided"),
    conf.level = 0.95, correct = TRUE) %>%
  broom::tidy()

homicide %>%
  group_by(city) %>%
  summarize(n_obs = n())
## 50 cities listed in dataset

#prop.tests for all cities
output = vector("city_state", length = 50 )

for (i in 1:50) {
  
  output[[i]] = prop.test(homicide[[i]])

}

    prop_each_city =
  purrr::map2(homicide$homi_unsolved, homicide$homi_total, prop.test) %>%
    unnest()

# CIs for Baltimore   
balt_test = 
  homicide %>%
  filter(city_state == "Baltimore, MD") %>%
  mutate(p_test = map2(homi_unsolved, homi_total, ~prop.test(.x, .y) %>%
    broom::tidy())) %>% 
    unnest()

balt_test %>%
  select(city_state, estimate, "CI_lower" = conf.low, "CI_upper" = conf.high)

# for all cities
all_cities = homicide %>%
   filter(city_state) %>%
  mutate(p_test = map2(homi_unsolved, homi_total, ~prop.test(.x, .y) %>%
    broom::tidy())) %>% 
    unnest()

all_cities %>%
  select(city_state, estimate, "CI_lower" = conf.low, "CI_upper" = conf.high)

# ploting CIs
homicides_lm = function(homicide) {
  lm(p_test ~ city_state, data = homicide)
    
}

homicides_lm(homicides_nest)[["data"]][[1:50]]

map(homicides_nest[["data"]], homicides__lm)

homicides_test %>% 
  homi_unsolved = fct_inorder(homi_unsolved) %>%
  mutate(
    model = map(data, homicides_lm)
  ) %>%
  geom_errorbar()
 
```
  
      
# Problem 3
```{r}
# for mu = 0
  norm_dist = tibble(
  x = rnorm(30, mean = 0, sd = 5)
  )

sim_mean_sd = function(n_obs, mu = 0, sigma = 5) {
  
  x = rnorm(n = n_obs, mean = mu, sd = sigma)

  tibble(
    mu_hat = mean(x),
    sigma_hat = sd(x)
    )
  
}

output = vector("list", length = 5000)

for (i in 1:5000) {
  
  output[[i]] = sim_mean_sd(n_obs = 30)
  
}

bind_rows(output) %>% 
  view

sim_results_df = 
  expand_grid(
    sample_size = 30,
    iteration = 1:5000
  ) %>% 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) %>% 
  unnest(estimate_df)

sim_function = function(n = 30, mu, sigma = 5) {
  sim_data = 
    tibble(
      x = rnorm(n, mean = mu, sd = sigma),)
  
  return(sim_data)
}

output = vector("list", length = 5000)

for (i in 1:5000) {
  output = bind_rows(output, sim_function(mu = 0))
}

t_test_mu0 = sim_results_mu0 %>%
  mutate(
    map(mu, t.test),
    map(broom::tidy),
    map(~select(.x, esimate, p.value))
  )

sim_results_df = 
  expand_grid(
    sample_size = 30,
    true_sigma = 5,
    true_mu = c(0, 1, 2, 3, 4, 5, 6),
    iteration = 1:5000
  ) %>% 
  mutate(
    estimate_df = 
      map2(.x = sample_size, .y = true_sigma, ~sim_mean_sd(n_obs = .x, sigma = .y))
  ) %>% 
  unnest(estimate_df)

t_test = sim_results_df %>%
    map(mu, t.test) %>%
    map(broom::tidy) %>%
    map(~select(.x, esimate, p.value))

# plotting all samples
sim_results_df %>% 
  mutate(
    sample_size = str_c("N = ", sample_size),
    sample_size = fct_inorder(true_mu)
  ) %>% 
  ggplot(aes(x = true_mu, y = p_value)) + 
  geom_violin() + 
  facet_grid(. ~ true_mu)

# plotting where null is rejected
sim_results_df %>% 
  filter(p_value < 0.5) %>%
  mutate(
    sample_size = str_c("N = ", sample_size),
    sample_size = fct_inorder(true_mu)
  ) %>% 
  ggplot(aes(x = true_mu, y = p_value)) + 
  geom_violin() + 
  facet_grid(. ~ true_mu)

```